Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-26 Docs/Paper/LaTex/template.tex
Fix 8.2 / Algorithms and Mail features

\begin{lstlisting}[caption=Pseudocode describing vZ,label=vZ-pseudocode]
01.#Initialize Variables
02.  Create vZ context 
03.  Create binary vector (x)
04.  Declare number of nodes, edges and S0
05.  Declare hardware cost of each node as array (h) 
06.  Declare software cost of each node as array (s)
07.  Declare communication cost of each edge (c)
08.  Declare transposed incidence matrix graph G (E)
09.#Arithmetic Expressions
10.  SC = s(1-x)
11.  CMC = c*|EX|
12.  Fobj =  x[i] * h[i]
13.#Assert Constraints
14.  Add constraints (SF + CMC <= S0)
15.  Add constraints to minimize Fobj
16.  Check Model
17.  Print Result
\end{lstlisting}

@@

\begin{lstlisting}[caption=Pseudocode describing ESBMC]
01. Initialize Variables 
02. Declare number of nodes and edges
03. Declare hardware cost of each node as array (h)
04. Declare software cost of each node as array (s)
05. Declare communication cost of each edge (c)
06. Declare the initial software cost of (S0)
07. Declare transposed incidence matrix graph G (E)
08. Define the solutions variable (Xi) as Boolean
09. main {
10.  for TipH = 0 to Hmax do {
11.   populate Xi with nondeterministic/test values
12.   Calculate s(1-x)+c|Ex| and store at variable
13.   Requirement isured by Assume (Variable <= S0)
14.   Calculate Hp cost Based on value tested of Xi
15.   Violation check with Assert(Hp > TipH)
16.  }
17. }
\end{lstlisting}

@@

\textcolor{blue}{Nao existe uma secao sobre o ESBMC PS. Ela esta misturada na secao do PB. Sugiro criar uma subsecao para o ESBMC PS. Feito}

@@

\textcolor{blue}{Falta descrever os resultados da melhor abordagem do ESBMC quando comparado ao vZ e ILP.}

>>>>

\begin{lstlisting}[caption=Pseudocode describing vZ,label=vZ-pseudocode, mathescape]
01.#Initialize Variables
02.  Create vZ context 
03.  Create binary vector (x)
04.  Declare number of nodes, edges and $S_{0}$
05.  Declare hardware cost of each node as array (h) 
06.  Declare software cost of each node as array (s)
07.  Declare communication cost of each edge (c)
08.  Declare transposed incidence matrix graph G (E)
09.#Arithmetic Expressions
10.  SC = s(1-x)
11.  CMC = c*|EX|
12.  Fobj =  x[i] * h[i]
13.#Assert Constraints
14.  Add constraints (SF + CMC <= $S_{0}$)
15.  Add constraints to minimize Fobj
16.  Check Model
17.  Print Result
\end{lstlisting}

@@

\begin{lstlisting}[caption=Pseudocode describing ESBMC, mathescape]
01. Initialize Variables 
02. Declare number of nodes and edges
03. Declare hardware cost of each node as array (h)
04. Declare software cost of each node as array (s)
05. Declare communication cost of each edge (c)
06. Declare the initial software cost of ($S_{0}$)
07. Declare transposed incidence matrix graph G (E)
08. Define the solutions variable ($X_{i}$ ) as Boolean
09. main {
10.  for TipH = 0 to Hmax do {
11.   populate $X_{i}$ with nondeterministic/test values
12.   Calculate s(1-x)+c|$E_{x}$| and store at variable
13.   Requirement isued by Assume (Variable <= $S_{0}$)
14.   Calculate Hp cost Based on value tested of $X_{i}$
15.   Violation check with Assert($H_{p}$ > TipH)
16.  }
17. }
\end{lstlisting}

@@

@@

\textcolor{red}{A versão PB do ESBMC descrita Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}, demonstra um avanco significativo na ferramenta; quando a quantidade de nós é baixa, em torno de 30, ESBMC-PB não demonstra eficiencia frente as tecnicas usadas em vZ e ILP, contudo, em torno de 150 nós, ESBMC se torna 3 vezes mais rapido do que ILP (A tecnicas mais robusta apresentada aqui). vZ para pequeno nós foi 30 vezes mais rapido (CRC32) do que ESBMC-PB e para nós intermediarios esse valor caiu para aproximadmente 1.9 (Clustering). Quando analisados os algoritmos RC6, Fuzzy e Mars, ESBMC-PB obteve TO ou MO em todos os casos. Os resultados são promissores levando em consideracao que as ferramentas vZ e Matlab são estados da arte em suas respectivas funcoes. }
